Revision Plan for SIGCOMM'24 Paper \#293

### 2024-06-04 revision_plan.tex
update after draft

@@

@@

\noindent\textcolor{blue}{\textbf{Response 3:} 
PPT's performance benefits are steamed from the following points. First, DCTCP contains spare bandwidth in slow start phase, which is obvious.
Second, in queue build-up phase, DCTCP also contains some spare bandwidth. We have already shown this point using a preliminarily experiment in Fig.1. But the reviewer may consider this experiment only contains synchronized bursts. Actually, in this experiment, the flows are generated according to Poisson arrival  pattern. So, there are both synchronized and nonsynchronized cases. We plan to clarify this point in our paper.
Finally, PPT uses a mirror-symmetric packet tagging design. This makes PPT achieve comparable performance on the average FCT of small flows.
}

@@

\noindent\textcolor{blue}{\textbf{Response 4:} 
We actually are not claiming that ``integration with other transports is easy".
What we claim is that the design of PPT can be integrated with delay-based transport.
We have already justified this point in our submission.
First, we have already implemented a delay-based transport conceptually equivalent to Swift in the ns3 simulator and showed that PPT's design can improve the performance of the original delay-based transport. Please see Fig. 26 for more details.
On the other hand, we have also discussed about the compatibility of PPT with other transports. Please see Appendix A for more details.
}

@@

\noindent\textcolor{blue}{\textbf{Response 5:}
We will complete the missing details about the experimental setup and parameters in the form of tables.
%We record the maximum value of the window from the beginning of the flow until now as MW (Maximum Window).
%Section 2.3 first shows how much DCTCP can benefit from padding the spare bandwidth to MW and plots the results in Figure 2.
%Moreover, we show that padding the spare bandwidth to MW is just suitable without wasting bandwidth or causing congestion throughout the experiment, and we plot the results of our experiment in Figure 3.
%Another question is about specific TCP send buffer thresholds.
%To reproduce the behavior of the actual deployed application as much as possible, we selected specific application traces for the Memcached application and the web server application, respectively.
%The flow size distribution in specific application traces is concentrated in particular intervals, e.g., there is no flow in the ETC trace of the paper[8] that exceeds 100KB.
%Under such traces, we set different thresholds depending on the traces to verify the effectiveness of the buffer-aware flow identification.
%In the large-scale simulation and testbed, the TCP send buffer threshold is set to the fixed value of 100KB, with outstanding results.
%To evaluate if this can benefit PPT’s performance, we construct a PPT variant that turns off this approach and considers all flows non-identified.
%We plot the results in Figure 20, showing that this improves the small flow performance as expected.
%In summary, the TCP send buffer threshold does not assume that the application type and flow size distribution are known a priori and effectively improves small flow performance.
}

@@

@@

@@

@@

@@

\textcolor{blue}{
On the other hand, PPT will open an LCP loop for each of the flow in flows 2$\sim$11 (if they are identified as small flows) to let them send opportunistic packets. However, these opportunistic packets may be queued or dropped due to buffer overflow, thus their LCP loops will be closed in a short while.
} 
%PPT actually will not send the opportunity packet when 10 more flows arrive.
%Specifically, traffic bursts result in more ECN-marked packets.
%The value of $\alpha$ increases due to Eq. (1), when PPT will not send any opportunity packets.

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

\noindent\textcolor{red}{\textbf{Proposed modification: }
Our experiments indeed demonstrate that our approach delivers comparable performance to proactive transports while remaining readily deployable. Therefore, we will not add further explanations or analyses in the paper. 
To address the reviewers' possible misunderstandings regarding the flow scheduling scheme, we have added a summary at the end of section 2 on page 5.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We have discussed PCC Proteus and other related work in the Appendix B on page 15.
}

@@

\noindent\textcolor{blue}{\textbf{Response 3:} 
PPT's performance benefits are steamed from the following points. First, DCTCP contains spare bandwidth in slow start phase, which is obvious.
Second, in queue build-up phase, DCTCP also contains some spare bandwidth. We have already shown this point using a preliminarily experiment in Fig.1. But the reviewer may consider this experiment only contains synchronized bursts. Actually, in this experiment, the flows are generated according to Poisson arrival  pattern. So, there are both synchronized and nonsynchronized cases. We plan to clarify this point in our paper.
Finally, PPT uses a mirror-symmetric packet tagging design. This makes PPT achieve comparable performance on the average FCT of small flows.
}
\noindent\textcolor{red}{\textbf{Proposed modification: }
We have added remark paragraph in section 2.3 on page 4 to show more insights.
}

@@

\noindent\textcolor{blue}{\textbf{Response 4:} 
We actually are not claiming that "integration with other transports is easy".
What we claim is that the design of PPT can be integrated with delay-based transport.
We have already justified this point in our submission.
First, we have already implemented a delay-based transport conceptually equivalent to Swift in the ns3 simulator and showed that PPT's design can improve the performance of the original delay-based transport. Please see Fig. 26 for more details.
On the other hand, we have also discussed about the compatibility of PPT with other transports. Please see Appendix A for more details.
}

\noindent\textcolor{red}{\textbf{Proposed modification: }
As relevant experiments and analyses have already been included in the paper, we will not add further discussion.
}

@@

\noindent\textcolor{blue}{\textbf{Response 5:}
We will complete the missing details about the experimental setup and parameters in the form of tables.
}

\noindent\textcolor{red}{\textbf{Proposed modification: }
We have added a table to fill in the missing parameters on page 15.
}
%We record the maximum value of the window from the beginning of the flow until now as MW (Maximum Window).
%Section 2.3 first shows how much DCTCP can benefit from padding the spare bandwidth to MW and plots the results in Figure 2.
%Moreover, we show that padding the spare bandwidth to MW is just suitable without wasting bandwidth or causing congestion throughout the experiment, and we plot the results of our experiment in Figure 3.
%Another question is about specific TCP send buffer thresholds.
%To reproduce the behavior of the actual deployed application as much as possible, we selected specific application traces for the Memcached application and the web server application, respectively.
%The flow size distribution in specific application traces is concentrated in particular intervals, e.g., there is no flow in the ETC trace of the paper[8] that exceeds 100KB.
%Under such traces, we set different thresholds depending on the traces to verify the effectiveness of the buffer-aware flow identification.
%In the large-scale simulation and testbed, the TCP send buffer threshold is set to the fixed value of 100KB, with outstanding results.
%To evaluate if this can benefit PPT’s performance, we construct a PPT variant that turns off this approach and considers all flows non-identified.
%We plot the results in Figure 20, showing that this improves the small flow performance as expected.
%In summary, the TCP send buffer threshold does not assume that the application type and flow size distribution are known a priori and effectively improves small flow performance.

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
To address the reviewers' possible misunderstandings regarding the flow scheduling scheme, we have added a summary at the end of section 2 on page 5.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
Since we have already explained this in detail in the paper, we will not include further explanations.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We have discussed PCC Proteus in other related work section on page 15.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
As the paper already includes detailed analyses of the performance benefits of PPT, we will not add additional discussion. 
To address the reviewers' possible misunderstandings regarding the flow scheduling scheme, we have added a summary at the end of section 2 on page 5.
}

@@

\textcolor{blue}{
On the other hand, PPT will open an LCP loop for each of the flow in flows 2$\sim$11 (if they are identified as small flows) to let them send opportunistic packets. However, these opportunistic packets may be queued or dropped due to buffer overflow, thus their LCP loops will be closed in a short while.
}

\noindent\textcolor{red}{\textbf{Proposed modification: }
We will not analyse this extreme case further in the paper.
}
%PPT actually will not send the opportunity packet when 10 more flows arrive.
%Specifically, traffic bursts result in more ECN-marked packets.
%The value of $\alpha$ increases due to Eq. (1), when PPT will not send any opportunity packets.

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
As the paper already contains a detailed analysis of the $\alpha_{min}$, we will not add further explanations
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We have added an analysis in the footnote on page 6.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We have added a new simulation with 100/400G topology to demonstrate this point. The results and analysis of this experiment have been presented in Appendix C on page 18 of the paper.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We will not add further discussion as the appendix has already contained relevant experiments.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We will add more intuitive reasons in Section 6.2 on page 12.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
As we have already explained the motivation in section 2.3, we will not add further explanations.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We have discussed Swift and Timely in other related work section on page 15 and show more details about the actual algorithm in the footnotes on page 17.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
As it has been analyzed in Section 6.1.1, we will not add further explanations.
}
